---
title       : Word Prediction Based on Natural Language Processing
subtitle    : 
author      : Andras Pap 
job         : Coursera Student for Data Science Specialization
logo        : ALP_Logo4.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## My Shiny App: Word Predictor

It predicts the next word the user about to type in based on preceeding words and a statistical model that was trained on data sets from twitter and news blogs.
You can find my useful Shiny data product at: https://andraspap.shinyapps.io/NLP-Demo-Project/ 
The training data can be found at: https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

Give it a try!!

--- .class #id 

## Word candidates are shown in a word cloud

```{r echo=FALSE, cache=TRUE}
	library(png)

	#Replace the directory and file information with your info
	ima <- readPNG('assets/img/wordcloud.png')
	
	#Set up the plot area
	plot(1:2, type='n', main="", xlab="", ylab="", xaxt='n', yaxt='n')
	lim <- par()
	rasterImage(ima, lim$usr[1], lim$usr[3], lim$usr[2], lim$usr[4])
```

--- .class #id 

## Documentation tab helps users
```{r echo=FALSE}
	library(png)

	#Replace the directory and file information with your info
	ima <- readPNG('assets/img/Documentation.png')
	
	#Set up the plot area
	plot(1:2, type='n', main="", xlab="", ylab="", xaxt='n', yaxt='n')
	lim <- par()
	rasterImage(ima, lim$usr[1], lim$usr[3], lim$usr[2], lim$usr[4],interpolate=FALSE)
```

--- .class #id 

## Thank You


Thank You for listening to me!

Check out my app: https://andraspap.shinyapps.io/NLP-Demo-Project/

Download it from: https://github.com/andraspap/DevelopingDataProducts_ShinyApp



