---
title       : Word Prediction Based on Natural Language Processing
subtitle    : 
author      : Andras Pap 
job         : Coursera Student for Data Science Specialization
logo        : ALP_Logo4.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## My Shiny App: Word Predictor

It predicts the next word the user about to type in based on preceeding words and a statistical model that was trained on data sets from twitter and news blogs.
You can find my useful Shiny data product at: https://andraspap.shinyapps.io/NLP-Demo-Project/ 
The training data can be found at: https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

Give it a try!!

--- .class #id 

## Prediction Is Based on the "mtcars" Data Set
The first 15 of the 32 cars in the data set:
```{r echo=FALSE}
data(mtcars)
head(mtcars,15)
```

--- .class #id 

## Clear Graphs Show the Result

```{r echo=FALSE, cache=TRUE}
lmBoth <- lm(mpg ~ disp + am + disp * am, mtcars)

plot(mpg ~ disp,mtcars,col = (mtcars$am == 0)*2 + 2, main = "MPG v.s. Displacement", ylab = "mpg", xlab = "Displacement (cu in.)")
abline(c(lmBoth$coef[1],lmBoth$coef[2]),col='blue')		
abline(c(lmBoth$coef[1] + lmBoth$coef[3],lmBoth$coef[2] + lmBoth$coef[4]),col='red')
legend("topright",lty = 1, seg.len = 2, xjust = 20, col=c("blue","red"),legend = c("automatic","manual"))
```

--- .class #id 

## Thank You


Thank You for listening to me!

Check out my app: https://andraspap.shinyapps.io/NLP-Demo-Project/

Download it from: https://github.com/andraspap/DevelopingDataProducts_ShinyApp



